---
title: "SimpleExample"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SimpleExample}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CVRTSEncoder)
```

Re-encode a set of categorical columns as a set of columns that are mutually useful for classification.  

The concept is y-aware encoding the trajectory of non-linear model residuals in terms of target categorical variables.

The idea is an extension of the [`vtreat`](https://github.com/WinVector/vtreat) coding [concepts](https://github.com/WinVector/vtreat/blob/master/extras/vtreat.pdf) and of the y-aware scaling concepts of Nina Zumel and John Mount:

  * [Principal Components Regression, Pt.1: The Standard Method](http://www.win-vector.com/blog/2016/05/pcr_part1_xonly/)
  * [Principal Components Regression, Pt. 2: Y-Aware Methods](http://www.win-vector.com/blog/2016/05/pcr_part2_yaware/)
  * [Principal Components Regression, Pt. 3: Picking the Number of Components](http://www.win-vector.com/blog/2016/05/pcr_part3_pickk/)
  * [y-aware scaling in context](http://www.win-vector.com/blog/2016/06/y-aware-scaling-in-context/).

```{r example}
data <- iris
avars <- c("Sepal.Length", "Petal.Length")
evars <- c("Sepal.Width", "Petal.Width")
dep_var <- "Species"
dep_target <- "versicolor"
for(vi in evars) {
  data[[vi]] <- as.character(round(data[[vi]]))
}
cross_enc <- estimate_residual_encoding_c(
  data = data,
  avars = avars,
  evars = evars,
  fit_predict = xgboost_fit_predict_c,
  dep_var = dep_var,
  dep_target = dep_target,
  n_comp = 4
)
enc <- prepare(cross_enc$coder, data)
data <- cbind(data, enc)
newvars <- c(avars, colnames(enc))
f <- wrapr::mk_formula(dep_var, newvars, outcome_target = dep_target)
model <- glm(f, data = data, family = binomial)
summary(model)

data$pred <- predict(model, newdata = data, type = "response")
table(data$Species, data$pred>0.5)
```

